Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-04-28 awipev-CO2.Rmd
removed duplicate salinity graph

d_all$diff_sal_fb_insitu_9m <- d_all$sal_insitu_ctd_9m - d_all$sal_fb
mean_diff_sal_fb_insitu_9m <- round(mean(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
sd_diff_sal_fb_insitu_9m <- round(sd(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)

### Plotly
# p_p_sal_fb_ctd <- ggplotly(p_sal_fb_ctd,dynamicTicks = TRUE)
# filename.html <- paste0("p_p_sal_fb_ctd.html")
# saveWidget(p_p_sal_fb_ctd, filename.html, selfcontained = T, libdir = "lib")

# #Plot for philipp
# sal_15 <- ggplot(data= d_all%>%dplyr::filter(datetime > "2015-10-01 00:00:00" & datetime < "2015-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
# geom_point(aes(y=sal_fb,col="FB") , size=2) +
# geom_point(aes(y=sal_insitu, col="in situ"))  +
# labs(title=  "salinity 2015", x = "Time", y= "")
# 
# sal_19 <-ggplot(data= d_all%>%dplyr::filter(datetime > "2019-10-01 00:00:00" & datetime < "2019-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
# geom_point(aes(y=sal_fb,col="FB") , size=2) +
# geom_point(aes(y=sal_insitu, col="in situ"))  +
# labs(title=  "salinity 2019", x = "Time", y= "")
# 
# ggsave("figures/sal_2019.png", sal_19, units="cm")
# ggsave("figures/sal_2015.png", sal_15, units="cm")
# ggsave("figures/sal_property.png", p_sal_fb_sal_insitu, units="cm")

```{r Sal plots, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}

sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, sal_mix, sal_fb)
sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
  dySeries("sal_fb", color = "grey", strokeWidth = 0, label = "sal_fb") %>%

dySeries("sal_mix", color = "black", strokeWidth = 0, label = "sal_mix") %>%

      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
    dyAxis("y",valueRange = c(30, 37)) %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
```

>>>>

d_all$diff_sal_fb_insitu_9m <- d_all$sal_insitu_ctd_9m - d_all$sal_fb
mean_diff_sal_fb_insitu_9m <- round(mean(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
sd_diff_sal_fb_insitu_9m <- round(sd(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
```
